\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-05-07 analysis/paper/paper.Rmd
combine ci and brier plots
We still need to fix the legends and the size of the figures, but this can be done at a later time.

In Figure\ref{fig:baselines}, we can see that all Cox models have similar average survival curves. On the other hand, Figure \ref{fig:brier1} shows that the full model has the lowest Brier score overall. For this reason, we will use this model in our comparison between regularized Cox regression, Kaplan-Meier estimation, and the approach from \pkg{casebase}.

@@

```{r baselines, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:baselines} Cumulative Incidence curves estimated using Cox regression and Kaplan-Meier (K-M)."}
ggplot(baseCoxComparisonData, aes(Time)) +
  geom_line(aes(y = APS, colour = "APS"), lwd = 1) +
  geom_line(aes(y = Full, col = "Full"), lwd = 1) +
  geom_line(aes(y = SPS, colour = "SPS"), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M"))
```

```{r brierpt1, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:brier1} Time-dependent Brier scores."}
# Extract time points
times <- sort(unique(test$d.time))
# Compute Brier scores
brierAPS <- Score(list("PredictionModel" = coxAPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
brierSPS <- Score(list("PredictionModel" = coxSPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

@@

ggplot(data = brierPlotter, mapping = aes(x = times, y = brierScore, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  labs(color = "Models") +
  # ggtitle("Brier scores over time") +
  scale_color_manual(values = q4[1:3])
```

@@

```{r coefplots, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3lolliPlot} A lollipop plot demonstrating the estimated coefficients between the following three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity."}
library(dotwhisker)
library(broom)
library(dplyr)

@@

These values do not inform us of model performance. To do so, we take our hazard functions and use them to predict the absolute risk of everyone in our test set, over time. The probabilities over time for each individual are averaged, resulting in the absolute risk curves in Figure \ref{fig:cs3Final}. There is separation between the curves, but it is minimal. To better demonstrate the differences in performance between the models, we compare Brier scores over time. In Figure \ref{fig:cs3FinalBrier}, the Brier score is lower in our penalized logistic regression model compared to both Cox regression models. However, this difference is minimal. On the other hand, all three models outperform the Kaplan-Meier model.

```{r cs3Final, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3Final} Four Cumulative Incidence curves."}
ggplot(ab, aes(Time)) +
  geom_line(data = baseCoxComparisonData, mapping = aes(y = Full, colour = "Cox"), lwd = 1) +
  geom_line(aes(y = absRisk, colour = Model), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  # ggtitle("Absolute risk curves") +
  scale_color_manual(values = q4, breaks = c("Cox", "Penalized Cox", "Penalized logistic", "K-M"))
```

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} Four curves comparing the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.", warning = FALSE}
# Compute Brier score for penalized models
brierFinalResults <- Score(list("Penalized Cox" = coxNet, "Penalized Logistic" = cbFull),
                           data = cbind(subset(test, select = c(d.time, death)),
                                        as.data.frame(newx)), 
                           formula = Hist(d.time, death != 0) ~ 1, summary = NULL, 
                           se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# Combine Brier scores between unpenalized and penalized models before plotting
data_brier <- bind_rows(
  brierFinalResults$Brier$score,
  filter(brierFull$Brier$score, model == "PredictionModel")
  ) %>% 
  mutate(model = case_when(
    model == "Null model" ~ "K-M",
    model == "PredictionModel" ~ "Cox",
    TRUE ~ model
  ),
  model = factor(model, levels = c("Cox", "Penalized Cox", "Penalized Logistic", "K-M")))

ggplot(data = data_brier, mapping = aes(x = times, y = Brier, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  # ggtitle("Brier score over time") +
  labs(color = "Models") +
  scale_color_manual(values = q4)
```

>>>>

In Figure\ref{fig:brier1} (A), we can see that all Cox models have similar average survival curves. On the other hand, Figure \ref{fig:brier1} (B) shows that the full model has the lowest Brier score overall. For this reason, we will use this model in our comparison between regularized Cox regression, Kaplan-Meier estimation, and the approach from \pkg{casebase}.

@@

```{r baselines, echo=FALSE, eval=eval_cs3}
cox_ci <- ggplot(baseCoxComparisonData, aes(Time)) +
  geom_line(aes(y = APS, colour = "APS"), lwd = 1) +
  geom_line(aes(y = Full, col = "Full"), lwd = 1) +
  geom_line(aes(y = SPS, colour = "SPS"), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M"))
```

```{r brierpt1, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:brier1} Comparison of three Cox regression models. (A) Cumulative Incidence curves. (B) Time-dependent Brier scores."}
# Extract time points
times <- sort(unique(test$d.time))
# Compute Brier scores
brierAPS <- Score(list("PredictionModel" = coxAPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
brierSPS <- Score(list("PredictionModel" = coxSPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

@@

cox_brier <- ggplot(data = brierPlotter, mapping = aes(x = times, y = brierScore, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  labs(color = "Models") +
  # ggtitle("Brier scores over time") +
  scale_color_manual(values = q4[1:3])

# Combine both plots using cowplot
plot_row <- cowplot::plot_grid(cox_ci + theme(legend.position = 'none'),
                               cox_brier + theme(legend.position = 'none'),
                               labels = c("A", "B"))
legend <- cowplot::get_legend(
  # create some space to the left of the legend
  cox_ci + theme(legend.box.margin = margin(0, 0, 0, 12))
)

cowplot::plot_grid(plot_row, legend, rel_widths = c(3, .4))
```

@@

```{r coefplots, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity."}
library(dotwhisker)
library(broom)
library(dplyr)

@@

These values do not inform us of model performance. To do so, we take our hazard functions and use them to predict the absolute risk of everyone in our test set, over time. The probabilities over time for each individual are averaged, resulting in the absolute risk curves in Figure \ref{fig:cs3FinalBrier} (A). There is separation between the curves, but it is minimal. To better demonstrate the differences in performance between the models, we compare Brier scores over time. In Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our penalized logistic regression model compared to both Cox regression models. However, this difference is minimal. On the other hand, all three models outperform the Kaplan-Meier model.

```{r cs3Final, echo=FALSE, eval=eval_cs3}
reg_ci <- ggplot(ab, aes(Time)) +
  geom_line(data = baseCoxComparisonData, mapping = aes(y = Full, colour = "Cox"), lwd = 1) +
  geom_line(aes(y = absRisk, colour = Model), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  # ggtitle("Absolute risk curves") +
  scale_color_manual(values = q4, breaks = c("Cox", "Penalized Cox", "Penalized logistic", "K-M"))
```

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} Four curves comparing the Cumulative Incidence (A) and the Brier scores (B) as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.", warning = FALSE}
# Compute Brier score for penalized models
brierFinalResults <- Score(list("Penalized Cox" = coxNet, "Penalized Logistic" = cbFull),
                           data = cbind(subset(test, select = c(d.time, death)),
                                        as.data.frame(newx)), 
                           formula = Hist(d.time, death != 0) ~ 1, summary = NULL, 
                           se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# Combine Brier scores between unpenalized and penalized models before plotting
data_brier <- bind_rows(
  brierFinalResults$Brier$score,
  filter(brierFull$Brier$score, model == "PredictionModel")
  ) %>% 
  mutate(model = case_when(
    model == "Null model" ~ "K-M",
    model == "PredictionModel" ~ "Cox",
    TRUE ~ model
  ),
  model = factor(model, levels = c("Cox", "Penalized Cox", "Penalized Logistic", "K-M"),
                 labels = c("Cox", "Pen. Cox", "Pen. Logistic", "K-M")))

reg_brier <- ggplot(data = data_brier, mapping = aes(x = times, y = Brier, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  # ggtitle("Brier score over time") +
  labs(color = "Models") +
  scale_color_manual(values = q4)

# Combine both plots using cowplot
plot_row_reg <- cowplot::plot_grid(reg_ci + theme(legend.position = 'none'),
                                   reg_brier + theme(legend.position = 'none'),
                                   labels = c("A", "B"))
legend_reg <- cowplot::get_legend(
  # create some space to the left of the legend
  reg_ci + theme(legend.box.margin = margin(0, 0, 0, 12))
)

cowplot::plot_grid(plot_row_reg, legend_reg, rel_widths = c(3, .4))
```

### 2020-05-07 analysis/paper/paper.tex
combine ci and brier plots
We still need to fix the legends and the size of the figures, but this can be done at a later time.

In Figure\ref{fig:baselines}, we can see that all Cox models have
similar average survival curves. On the other hand, Figure
\ref{fig:brier1} shows that the full model has the lowest Brier score
overall. For this reason, we will use this model in our comparison
between regularized Cox regression, Kaplan-Meier estimation, and the
approach from \pkg{casebase}.

{\centering \includegraphics{../figures/baselines-1}

\caption{\label{fig:baselines} Cumulative Incidence curves estimated using Cox regression and Kaplan-Meier (K-M).}\label{fig:baselines}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:brier1} Time-dependent Brier scores.}\label{fig:brierpt1}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:cs3lolliPlot} A lollipop plot demonstrating the estimated coefficients between the following three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

These values do not inform us of model performance. To do so, we take
our hazard functions and use them to predict the absolute risk of
everyone in our test set, over time. The probabilities over time for
each individual are averaged, resulting in the absolute risk curves in
Figure \ref{fig:cs3Final}. There is separation between the curves, but
it is minimal. To better demonstrate the differences in performance
between the models, we compare Brier scores over time. In Figure
\ref{fig:cs3FinalBrier}, the Brier score is lower in our penalized
logistic regression model compared to both Cox regression models.
However, this difference is minimal. On the other hand, all three models
outperform the Kaplan-Meier model.

{\centering \includegraphics{../figures/cs3Final-1}

\caption{\label{fig:cs3Final} Four Cumulative Incidence curves.}\label{fig:cs3Final}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:cs3FinalBrier} Four curves comparing the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-05-05 17:12:52 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.0 (2020-04-24)
#> Platform: x86_64-apple-darwin17.0 (64-bit)
#> Running under: macOS Catalina 10.15.4
#> 
#> Matrix products: default
#> BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib
#> LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
#> 
#> locale:
#> [1] en_CA.UTF-8/en_CA.UTF-8/en_CA.UTF-8/C/en_CA.UTF-8/en_CA.UTF-8
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.5.6               dotwhisker_0.5.0         
#>  [3] colorspace_1.4-1          prodlim_2019.11.13       
#>  [5] riskRegression_2020.02.05 pracma_2.2.9             
#>  [7] kableExtra_1.1.0          data.table_1.12.8        
#>  [9] glmnet_3.0-2              Matrix_1.2-18            
#> [11] casebase_0.2.1.9001       survival_3.1-12          
#> [13] magrittr_1.5              forcats_0.5.0            
#> [15] stringr_1.4.0             dplyr_0.8.5              
#> [17] purrr_0.3.4               readr_1.3.1              
#> [19] tidyr_1.0.2               tibble_3.0.1             
#> [21] ggplot2_3.3.0             tidyverse_1.3.0          
#> 
#> loaded via a namespace (and not attached):
#>  [1] nlme_3.1-147        fs_1.4.1            cmprsk_2.2-9       
#>  [4] lubridate_1.7.8     rms_5.1-4           webshot_0.5.2      
#>  [7] RColorBrewer_1.1-2  httr_1.4.1          numDeriv_2016.8-1.1
#> [10] tools_4.0.0         backports_1.1.6     R6_2.4.1           
#> [13] rpart_4.1-15        Hmisc_4.4-0         DBI_1.1.0          
#> [16] mgcv_1.8-31         nnet_7.3-13         withr_2.2.0        
#> [19] gridExtra_2.3       tidyselect_1.0.0    compiler_4.0.0     
#> [22] quantreg_5.55       cli_2.0.2           rvest_0.3.5        
#> [25] htmlTable_1.13.3    SparseM_1.78        xml2_1.3.2         
#> [28] sandwich_2.5-1      labeling_0.3        checkmate_2.0.0    
#> [31] scales_1.1.0        mvtnorm_1.1-0       polspline_1.1.17   
#> [34] digest_0.6.25       foreign_0.8-78      rmarkdown_2.1      
#> [37] base64enc_0.1-3     rticles_0.14        jpeg_0.1-8.1       
#> [40] pkgconfig_2.0.3     htmltools_0.4.0     dbplyr_1.4.3       
#> [43] htmlwidgets_1.5.1   rlang_0.4.5         readxl_1.3.1       
#> [46] rstudioapi_0.11     VGAM_1.1-2          farver_2.0.3       
#> [49] shape_1.4.4         generics_0.0.2      zoo_1.8-7          
#> [52] jsonlite_1.6.1      acepack_1.4.1       Formula_1.2-3      
#> [55] Rcpp_1.0.4.6        munsell_0.5.0       fansi_0.4.1        
#> [58] lifecycle_0.2.0     multcomp_1.4-13     stringi_1.4.6      
#> [61] yaml_2.2.1          MASS_7.3-51.5       plyr_1.8.6         
#> [64] ggstance_0.3.4      grid_4.0.0          crayon_1.3.4       
#> [67] lattice_0.20-41     haven_2.2.0         hms_0.5.3          
#> [70] timereg_1.9.4       knitr_1.28          pillar_1.4.3       
#> [73] codetools_0.2-16    stats4_4.0.0        reprex_0.3.0       
#> [76] glue_1.4.0          evaluate_0.14       latticeExtra_0.6-29
#> [79] modelr_0.1.6        vctrs_0.2.4         png_0.1-7          
#> [82] foreach_1.5.0       MatrixModels_0.4-1  cellranger_1.1.0   
#> [85] gtable_0.3.0        assertthat_0.2.1    xfun_0.13          
#> [88] viridisLite_0.3.0   iterators_1.0.12    cluster_2.1.0      
#> [91] lava_1.6.7          TH.data_1.0-10      ellipsis_0.3.0
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    editMax /Users/maxturgeon/Documents/git_repos/cbpaper
#> Head:     [70115f2] 2020-04-22: Merge pull request #20 from Jesse-Islam/master
\end{CodeOutput}
\end{CodeChunk}

>>>>

In Figure\ref{fig:brier1} (A), we can see that all Cox models have
similar average survival curves. On the other hand, Figure
\ref{fig:brier1} (B) shows that the full model has the lowest Brier
score overall. For this reason, we will use this model in our comparison
between regularized Cox regression, Kaplan-Meier estimation, and the
approach from \pkg{casebase}.

@@

\caption{\label{fig:brier1} Comparison of three Cox regression models. (A) Cumulative Incidence curves. (B) Time-dependent Brier scores.}\label{fig:brierpt1}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

These values do not inform us of model performance. To do so, we take
our hazard functions and use them to predict the absolute risk of
everyone in our test set, over time. The probabilities over time for
each individual are averaged, resulting in the absolute risk curves in
Figure \ref{fig:cs3FinalBrier} (A). There is separation between the
curves, but it is minimal. To better demonstrate the differences in
performance between the models, we compare Brier scores over time. In
Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our
penalized logistic regression model compared to both Cox regression
models. However, this difference is minimal. On the other hand, all
three models outperform the Kaplan-Meier model.

@@

\caption{\label{fig:cs3FinalBrier} Four curves comparing the Cumulative Incidence (A) and the Brier scores (B) as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

This report was generated on 2020-05-07 08:27:50 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.0 (2020-04-24)
#> Platform: x86_64-apple-darwin17.0 (64-bit)
#> Running under: macOS Catalina 10.15.4
#> 
#> Matrix products: default
#> BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib
#> LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
#> 
#> locale:
#> [1] en_CA.UTF-8/en_CA.UTF-8/en_CA.UTF-8/C/en_CA.UTF-8/en_CA.UTF-8
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.5.6               dotwhisker_0.5.0         
#>  [3] colorspace_1.4-1          prodlim_2019.11.13       
#>  [5] riskRegression_2020.02.05 pracma_2.2.9             
#>  [7] kableExtra_1.1.0          data.table_1.12.8        
#>  [9] glmnet_3.0-2              Matrix_1.2-18            
#> [11] casebase_0.2.1.9001       survival_3.1-12          
#> [13] magrittr_1.5              forcats_0.5.0            
#> [15] stringr_1.4.0             dplyr_0.8.5              
#> [17] purrr_0.3.4               readr_1.3.1              
#> [19] tidyr_1.0.2               tibble_3.0.1             
#> [21] ggplot2_3.3.0             tidyverse_1.3.0          
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-2          ellipsis_0.3.0     
#>  [4] ggstance_0.3.4      htmlTable_1.13.3    base64enc_0.1-3    
#>  [7] fs_1.4.1            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-0      
#> [13] lubridate_1.7.8     xml2_1.3.2          codetools_0.2-16   
#> [16] knitr_1.28          Formula_1.2-3       jsonlite_1.6.1     
#> [19] cluster_2.1.0       dbplyr_1.4.3        png_0.1-7          
#> [22] compiler_4.0.0      httr_1.4.1          backports_1.1.6    
#> [25] assertthat_0.2.1    cli_2.0.2           acepack_1.4.1      
#> [28] htmltools_0.4.0     quantreg_5.55       tools_4.0.0        
#> [31] gtable_0.3.0        glue_1.4.0          Rcpp_1.0.4.6       
#> [34] cellranger_1.1.0    vctrs_0.2.4         nlme_3.1-147       
#> [37] iterators_1.0.12    xfun_0.13           rvest_0.3.5        
#> [40] lifecycle_0.2.0     polspline_1.1.17    MASS_7.3-51.5      
#> [43] zoo_1.8-7           scales_1.1.0        hms_0.5.3          
#> [46] sandwich_2.5-1      SparseM_1.78        RColorBrewer_1.1-2 
#> [49] rticles_0.14        yaml_2.2.1          gridExtra_2.3      
#> [52] rms_5.1-4           rpart_4.1-15        latticeExtra_0.6-29
#> [55] stringi_1.4.6       foreach_1.5.0       checkmate_2.0.0    
#> [58] lava_1.6.7          shape_1.4.4         rlang_0.4.5        
#> [61] pkgconfig_2.0.3     evaluate_0.14       lattice_0.20-41    
#> [64] htmlwidgets_1.5.1   labeling_0.3        cmprsk_2.2-9       
#> [67] cowplot_1.0.0       tidyselect_1.0.0    plyr_1.8.6         
#> [70] R6_2.4.1            generics_0.0.2      Hmisc_4.4-0        
#> [73] multcomp_1.4-13     DBI_1.1.0           pillar_1.4.3       
#> [76] haven_2.2.0         foreign_0.8-78      withr_2.2.0        
#> [79] mgcv_1.8-31         nnet_7.3-13         modelr_0.1.6       
#> [82] crayon_1.3.4        rmarkdown_2.1       timereg_1.9.4      
#> [85] jpeg_0.1-8.1        grid_4.0.0          readxl_1.3.1       
#> [88] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [91] numDeriv_2016.8-1.1 stats4_4.0.0        munsell_0.5.0      
#> [94] viridisLite_0.3.0
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    editMax /Users/maxturgeon/Documents/git_repos/cbpaper
#> Head:     [c6107b6] 2020-05-05: edit jesse's section
\end{CodeOutput}
\end{CodeChunk}
